When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2018-02-12 paper/paper.tex
Re-word what's in domains

In the case of subgraph isomorphism, the basic constraint model is to have a domain for each pattern
vertex, with the domains being each target vertex. An \emph{all-different} constraint ensures
injectivity, whilst the adjacency rules can be expressed as extensional constraints by listing
allowed tuples.  With this model, the backtracking search builds up partial assignments of pattern
vertices to target vertices, until either a complete assignment is reached (and the instance is
\emph{satisfiable}), or search establishes that no such assignment can exist (and it is
\emph{unsatisfiable}).

>>>>

In the case of subgraph isomorphism, the basic constraint model is to have a domain for each pattern
vertex, with each domain being the set of target vertices. An \emph{all-different} constraint ensures
injectivity, whilst the adjacency rules can be expressed as extensional constraints by listing
allowed tuples.  With this model, the backtracking search builds up partial assignments of pattern
vertices to target vertices, until either a complete assignment is reached (and the instance is
\emph{satisfiable}), or search establishes that no such assignment can exist (and it is
\emph{unsatisfiable}).
